A publishing infrastructure for AI-assisted academic authoring

### 2023-07-17 latex/manuscript.tex
rename introduction
add objective section

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

>>>>

\hypertarget{introduction}{%
\subsection{Introduction and background}\label{introduction}}

@@

\hypertarget{objective}{%
\subsection{Objective}\label{objective}}

This study has two objectives:
1) investigate how recently released large language models can reduce the time-consuming process of writing and revising scholarly manuscripts;
2) develop a workflow that integrates these models into the Manubot publishing ecosystem to transparently suggest revisions to improve the quality of the original text.
